\section*{Program Summary}

\noindent\textbf{Program title:} hidden-attractors-fo

\noindent\textbf{Archived title:} A Python Library for the Theoretical-Numerical Search and Localization of Hidden Attractors

\noindent\textbf{CPC Library link:} To be assigned after acceptance.

\noindent\textbf{Developer's repository link:} \url{https://github.com/Xerkkun/Hidden-Attractors-Localization}

\noindent\textbf{Licensing provisions:} MIT for the software package. Publication text, figures, and reports should keep their own licensing notes if separate terms are required.

\noindent\textbf{Programming language:} Python, with optional C backends.

\noindent\textbf{External routines/libraries:} NumPy, SciPy, Matplotlib, Numba, pytest for validation, optional antropy/nolds for diagnostics, and an optional C compiler for native backends.

\noindent\textbf{Supplementary material:} Archived software/material DOI: \url{https://doi.org/10.17605/OSF.IO/ZGK74}

\noindent\textbf{Nature of problem:} Theoretical-numerical search, localization, reproduction, audit, and conservative classification of candidate hidden attractors in integer- and commensurate fractional-order Chua/Lur'e systems. Fractional workflows use Caputo derivatives and explicit memory policies.

\noindent\textbf{Solution method:} Describing-function seeding, BDF-style algebraic continuation, integer-order integration paths, Caputo ABM/EFORK integration for fractional order, finite-time chaos diagnostics, and equilibrium-neighborhood tests around all equilibria.

\noindent\textbf{Restrictions:} The implemented promoted workflows target scalar Lur'e-compatible systems and commensurate fractional order in the fractional case. Numerical neighborhood tests provide finite-time evidence under tested neighborhoods; they do not certify global mathematical hiddenness.

\noindent\textbf{Unusual features:} The repository separates promoted validation evidence, local/regenerable outputs, legacy material, and editorial CPC preparation. The Chua arctan route is implemented algebraically but is pending full validation and is not promoted as a validated hidden attractor.

\noindent\textbf{Running time:} From seconds for metadata, CLI, and smoke checks to minutes or hours for long validation or fractional-memory sweeps, depending on horizon, step size, memory policy, backend, and sampling plan.

\noindent\textbf{References:} See \texttt{references.bib}.
